### 2021-04-08 papers/SYRCoSE/related.tex
SYRCoSE: fix TODOs

\todo{Fix Winskel1986 vs Winskel 1982 (introduction vs related work)}

Event structures were introduced by Winskel to study the semantics of 
the calculus of communicating systems~\cite{Winskel:82}. 
Several modifications of event structures~\cite{Langerak:91, Boudol-Castellani:1991}
were later proposed to tackle similar problems.

>>>>

Event structures were introduced by Winskel to study the semantics of 
the calculus of communicating systems~\cite{Winskel:86, Winskel:82}. 
Several modifications of event structures~\cite{Langerak:91, Boudol-Castellani:1991}
were later proposed to tackle similar problems.
